\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{xcolor}
\definecolor{accent}{HTML}{1565C0}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\input{glyphtounicode}

% Font options
% \usepackage[sfdefault]{roboto}  % Sans-serif font

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\large\bfseries\scshape\raggedright\color{accent}}{}{0em}{}[{\color{accent}\titlerule}]
\titlespacing*{\section}{0pt}{8pt}{4pt}

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-4pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.1in, label={}, topsep=4pt, itemsep=6pt, parsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  {\color{accent}\textbf{\Huge Javier Herrero Pérez}} \\[5pt]
  \small
  656\,181\,225 \textcolor{accent}{$\cdot$}
  \href{mailto:jherrerop88@gmail.com}{jherrerop88@gmail.com} \\[3pt]
  \href{https://www.linkedin.com/in/javier-herrero-p\%C3\%A9rez-ba672b271/}{linkedin.com/in/javier-herrero-pérez}
  \textcolor{accent}{$\cdot$}
  \href{https://github.com/hepejaAED}{github.com/hepejaAED}
  \textcolor{accent}{$\cdot$}
  \textbf{\href{https://hepejaaed.github.io/}{hepejaaed.github.io}}
\end{center}

\section{About me}
% I hold a degree in Physics from the University of Salamanca, with a strong foundation in mathematical modelling, statistics and data analysis. I am currently pursuing a Master’s degree in Data Science at the University of Valencia and have gained hands-on experience in applied data science during an internship at the AIR Institute, working on real-world AI and data projects.
% I have practical experience with Python, machine learning and natural language processing, and I am seeking junior roles in Data Science or related fields.
I studied Physics because I liked understanding how things work at a fundamental level. That same curiosity pulled me into Data Science and, more recently, into AI agents and LLM systems. I'm currently in my Master's at the University of Valencia, looking for a junior role where I can keep building: ideally on products that use language models or agentic workflows. I have real experience shipping ML pipelines from an internship at AIR Institute, and I'm particularly interested in Generative AI and LLM-based systems.


\section{Technical Skills}
\resumeSubHeadingList
    \resumeItem{\textbf{Programming}: Python, SQL, R, Fortran}
  \resumeItem{\textbf{Data \& ML Libraries}: NumPy, Pandas, Scikit-learn}
  \resumeItem{\textbf{Deep Learning Frameworks}: TensorFlow, PyTorch, Keras}
  \resumeItem{\textbf{MLOps \& Tools}: Git, AWS, Jupyter Notebook, MongoDB, Cassandra, LaTeX}
    \resumeItem{\textbf{Languages}: Spanish (native), English (B1+: Professional communication and technical proficiency)}
\resumeSubHeadingListEnd


\section{Experience}
\resumeSubHeadingList

\resumeSubheading
    {Data Scientist | Internship}{Jul 2024 -- Aug 2024}
    {AIR Institute (International Centre for Artificial Intelligence Research)}{Spain}
    \resumeSubHeadingList
        \resumeItem{\textbullet~\textbf{Workplace Risk Classification:} Took a real sensor dataset from scratch and put together a 6-class risk detection pipeline: feature engineering (temporal exposure, exponential decay weighting), SMOTE to handle a 27:1 imbalance, and a Random Forest that hit \textbf{100\% accuracy and macro F1 = 0.99} on a stratified 80/20 split. Used SHAP to explain the model and show that CO$_2$ and cumulative exposure time were the dominant drivers. Also trained an XGBoost regressor to predict CO$_2$ from environmental sensors, hitting \textbf{R$^2$ = 0.9999 and MAE = 27.74\,ppm} ($<$6\% error).}
        \resumeItem{\textbullet~\textbf{Candidate Profiling (NLP):} Built a feature extraction pipeline with Whisper and PySentimiento to pull tone, emotion and linguistic signals from candidate interviews; the features fed a shortlisting classifier and measurably improved its precision and recall.}
    \resumeSubHeadingListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingList

% \resumeSubheading
% {Multi-Agent System for Synchronous Energy Dispatch in Smart Grids}{Present}{}{}
% \resumeSubHeadingList
%     \resumeItem{{\small Developed a multi-agent framework using LangGraph to optimize synchronous power dispatch and grid stability under high renewable volatility (Python, TensorFlow, Transformers, statsmodels, LangGraph).}}
% \resumeSubHeadingListEnd

\resumeSubheading
{Clickbait Detection in News Headlines}{}{}{}
\resumeSubHeadingList
    \resumeItem{{\small Developed an NLP pipeline to detect clickbait using cosine similarity and topic modelling (Python, Scikit-learn, Transformers). Built a LangChain agent that autonomously scrapes news headlines and classifies them as clickbait or not in an end-to-end workflow.}}
\resumeSubHeadingListEnd

\resumeSubheading
{Calorie Estimation from Food Images}{}{}{}
\resumeSubHeadingList
    \resumeItem{{\small Built a deep learning pipeline to estimate calories from images using CNN models (Python, TensorFlow, Hugging Face).}}
\resumeSubHeadingListEnd

\resumeSubheading
{Exploratory Analysis of Labour Market Data}{}{}{}
\resumeSubHeadingList
    \resumeItem{{\small Performed EDA on Spanish labour market data to identify gender inequality patterns (R, tidyverse, ggplot2).}}
\resumeSubHeadingListEnd

\resumeSubHeadingListEnd

% \resumeSubheading
%     {Causal Inference on Lalonde Dataset}{2025}
%     {Causal Analysis Project}{Python, DoubleML, Scikit-learn}
%     \resumeSubHeadingList
%         \resumeItem{\textbullet\ Estimated treatment effects using causal inference techniques on observational data}
%         \resumeItem{\textbullet\ Applied propensity score matching, class balancing, and meta-learners}
%         \resumeItem{\textbullet\ Evaluated bias reduction and robustness of different causal models}
%     \resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingList

\resumeSubheading
    {Master’s in Data Science}{Sept 2025 - Jun 2026 (expected)}
    {University of Valencia}{Spain}
    \resumeSubHeadingList
        \resumeItem{\textbullet\ GPA: 8.86/10}
    \resumeSubHeadingListEnd

\resumeSubheading
    {Bachelor’s Degree in Physics}{Sept 2021 - Jul 2025}
    {University of Salamanca}{Spain}
    \resumeSubHeadingList
        \resumeItem{\textbullet\ GPA: 7.25/10}
    \resumeSubHeadingListEnd


\resumeSubHeadingListEnd



\end{document}